Efficient inference using the approximate Riemannian geometry of stochastic population models

### 2012-08-03 paper/paper.tex
Added timescales

\begin{abstract}
\begin{itemize}
\item We present efficient and novel methodology for Bayesian inference over stochastic kinetic models with complex dynamics and large numbers of parameters.

Inference for MJP is difficult: non-linear likelihood, computational
  expensive, proposals expensive, analytically intractable likelihood
\item Data: Partially observed discrete, noisy time-course.
\item Existing work for likelihood evaluations: 
\begin{itemize}
\item Likelihood calculations
\begin{itemize}
\item Exact: Boys et al, slow, not noise
\item Approx SDE - Andy and Darren (with Noise)
\item Approx MC - Andy and Colin (no noise)
\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
\end{itemize}
\item New:
\begin{itemize}
\item Approximate proposal mechanism based on the geometry of MC
\begin{itemize}
\item Overcome strong correlation structure which is standard with partially
  observed data
\item Fast proposals based on approximate geometry
\item Accept/reject with approximate model before trying exact model
\end{itemize}
\item Inference is exact
\item Including observational error
\item Time course measurements, unlike Mark's LNA
\end{itemize}
\end{itemize}
\end{itemize}
\end{abstract}

@@

\section{Introduction}
\label{s:intro}

@@

\begin{itemize}
\item Comparison between Riemannian MC proposal, LNA proposal and true proposal
\item Comparison between Riemannian and MH
\item A single example, with highly correlated parameters
\end{itemize}

@@

\begin{itemize}
\item Use model from Stumpf ABC paper (with real data?)
\end{itemize}

@@

\begin{itemize}
\item 36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments and 3 blocks, with interactions
\item 5*27 (I think) latent data sets
\item Exploit Sub-mannifolds for choosing parameter sets
\item Poisson error structure
\end{itemize}

>>>>

\begin{abstract}
Abstract
\end{abstract}

@@

\section{Useful Papers}

\begin{itemize}
\item Papers cited in \textbf{refs.bib}
\item Useful papers put in papers directory
\end{itemize}

\section{Introduction}
\label{s:intro}\textbf{31/8: BC/CSG}

@@

  \begin{itemize}
  \item Calculate exact proposal for comparison (\textbf{17/8: CSG})
  \item Construct LNA model for ID (\textbf{14/9: CSG/BC})
  \item Graphs:
    \begin{itemize}
    \item Data: \textbf{17/8: CSG}
    \item Geometry proposal: 3 proposals for the 3 derviates: k1\^2, k1k2, k2\^2
      \textbf{24/8: }
    \item Likelihood: Exact likelihood vs LNA vs MC \textbf{24/8: }
    \item Delay acceptance(?)
    \item Sampling efficiences M-H vs RM (appendix)
    \end{itemize}
  \end{itemize}

@@

    \begin{itemize}
    \item Construct moment equations (\textbf{17/8: CSG}) Lognormal?
    \item Construct proposal
    \item Delay acceptance
    \item Run experiments
    \item Graphs:
      \begin{itemize}
      \item Data
      \item Sampling efficiences M-H vs RM (appendix)
      \item Posterior compare to Stumpf
      \end{itemize}
    \end{itemize}

@@

\subsubsection{Introduction}

36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments
and 3 blocks, with interactions. 5*27 (I think) latent data sets. Exploit Sub-mannifolds for choosing parameter sets
Poisson error structure.

    \begin{itemize}
    \item Construct moment equations (appendix) \textbf{Done}
    \item Construct proposal (appendix)
    \item Delay acceptance
    \item Run experiments
    \item Graphs:
      \begin{itemize}
      \item Data \textbf{Done}
      \item Sampling efficiences M-H vs RM; ESS
      \item Posteriors
      \end{itemize}
    \end{itemize}
